\documentclass{beamer}
\usetheme{metropolis} % Using metropolis as it's clean and modern

\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{amssymb}

% Define TypeShift Colors
\definecolor{TypeShiftBG}{HTML}{111111}
\definecolor{TypeShiftPurple}{HTML}{AE81FF}
\definecolor{TypeShiftText}{HTML}{FFFFFF}
\definecolor{TypeShiftGray}{HTML}{666666}

% Set Beamer Colors
\setbeamercolor{background canvas}{bg=TypeShiftBG}
\setbeamercolor{normal text}{fg=TypeShiftText}
\setbeamercolor{frametitle}{bg=TypeShiftBG, fg=TypeShiftPurple}
\setbeamercolor{title}{fg=TypeShiftPurple}
\setbeamercolor{subtitle}{fg=TypeShiftText}
\setbeamercolor{section in head/foot}{fg=TypeShiftPurple}

% Customize blocks
\setbeamercolor{block title}{bg=TypeShiftPurple, fg=TypeShiftBG}
\setbeamercolor{block body}{bg=TypeShiftPurple!10, fg=TypeShiftText}

\title{TypeShift}
\subtitle{A WEB-BASED PLATFORM TO PRACTICE AND IMPROVE TYPING}
\author{TEAM MEMBERS: \\ 
Aditya Mishra (2400520100008) \\ 
Anushaka Prasad (2400520100020) \\ 
Harshit Yadav (2400520100038) \\ 
Devansh Singh (2400520100032) \\ 
Darshika Singh (2400520100029)}
\date{}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{Table of Contents}
    \begin{enumerate}
        \item Project Overview
        \item Comparison with Existing Systems
        \item Technologies and Tools Used
        \item Project Development Timeline
        \item Current Progress and Work Status
    \end{enumerate}
\end{frame}

\begin{frame}{Project Overview}
    TypeShift is a web-based tool built to help users track and improve their typing performance. The platform provides a focused environment for testing speed and accuracy, with a backend designed to store and display progress over time.
    \vfill
    \begin{columns}[t]
        \begin{column}{0.5\textwidth}
            \textbf{\color{TypeShiftPurple}Leaderboard:} Data-driven ranking. \\
            \textbf{\color{TypeShiftPurple}Typing Environment:} Core "testbox" area. \\
            \textbf{\color{TypeShiftPurple}Navigation Bar:} Quick access header.
        \end{column}
        \begin{column}{0.5\textwidth}
            \textbf{\color{TypeShiftPurple}Authentication:} Secure login/register. \\
            \textbf{\color{TypeShiftPurple}Dashboard:} Individual user stats. \\
            \textbf{\color{TypeShiftPurple}Live Settings:} On-the-fly mode switching.
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}{Project Comparison}
    \centering
    \small
    \begin{tabular}{lccc}
        \toprule
        \textbf{\color{TypeShiftPurple}Feature} & \textbf{TypeRacer} & \textbf{TypeShift} & \textbf{MonkeyType} \\
        \midrule
        Custom word lists & \color{red}$\times$ & \color{green}\checkmark & Limited \\
        Difficulty levels & \color{red}$\times$ & \color{green}\checkmark & Limited \\
        Personal progress graph & \color{red}$\times$ & \color{green}\checkmark & \color{green}\checkmark \\
        Leaderboard & \color{green}\checkmark & \color{green}\checkmark & \color{red}$\times$ \\
        Reaction on mistype & \color{red}$\times$ & \color{green}\checkmark & \color{red}$\times$ \\
        Login \& records & \color{green}\checkmark & \color{green}\checkmark & \color{green}\checkmark \\
        \bottomrule
    \end{tabular}
    \vfill
    \footnotesize \textit{Goal: Achieve these features after implementing a basic prototype.}
\end{frame}

\begin{frame}{Tools Used}
    \begin{description}
        \item[Frontend] JavaScript (ESM), React, HTML5, CSS3, Vite
        \item[Backend] Node.js, Express.js
        \item[Database] MongoDB
        \item[Other Tools] Git, GitHub
    \end{description}
    \vfill
    \begin{block}{Why Vite?}
        Fast development, instant hot module replacement (HMR), and optimized production builds.
    \end{block}
\end{frame}

\begin{frame}{Timeline of the Project}
    \begin{itemize}
        \item[\color{TypeShiftPurple}$\bullet$] \textbf{Week 1--2:} Planning \& Research
        \item[\color{TypeShiftPurple}$\bullet$] \textbf{Week 3--4:} Core Functionality Implementation
        \item[\color{TypeShiftPurple}$\bullet$] \textbf{Week 5--6:} UI Design \& Development
        \item[\color{TypeShiftPurple}$\bullet$] \textbf{Week 7--8:} Testing \& Finalization
    \end{itemize}
\end{frame}


\begin{frame}{Status of Work Done}
    \begin{columns}[t]
        \begin{column}{0.33\textwidth}
            \textbf{\color{green}COMPLETED}
            \begin{itemize}
                \scriptsize
                \item UI/Layout planning
                \item Core features list
                \item Figma prototype
                \item Navigation flow
            \end{itemize}
        \end{column}
        \begin{column}{0.33\textwidth}
            \textbf{\color{yellow}ONGOING}
            \begin{itemize}
                \scriptsize
                \item React components
            \end{itemize}
        \end{column}
        \begin{column}{0.33\textwidth}
            \textbf{\color{TypeShiftPurple}PLANNED}
            \begin{itemize}
                \scriptsize
                \item Backend/DB schema
                \item MongoDB integration
                \item Real-time logic
                \item Hosting
            \end{itemize}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \centering
    \Huge \color{TypeShiftPurple} The End
    \vfill
    \large THANK YOU FOR LISTENING
\end{frame}

\end{document}
